Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review

### 2021-11-04 _bookdown_files/06-conclusion.Rmd
Methodology

This review is the first Scoping Review to map the current knowledge in Syndemic Theory applied to MSM. We charted and presented detailed data regarding the way research has been done. As such, we offer a precious insight and actionable recommendations for the future of the field. Our search strategy of electronic databases was comprehensive and developed with the help of the director of health sciences library of our institution. We combined this database search with a secondary hand-search of references lists of the included studies. Moreover, we conducted a fully transparent and reproducible review. Other researchers may freely reuse our data and scripts to conduct their own work. To this end, we created a SQL database from our data. Other researchers may thus perform complex queries on our database of included studies to quickly identify studies relevant for their work (e.g. every study using the CESD to measure depression on Black MSM between 2014 and 2019).

>>>>

This review is the first Scoping Review to map the current knowledge in Syndemic Theory applied to MSM. We charted and presented detailed data regarding the way research has been done. As such, we offer a precious insight and actionable recommendations for the future of the field. Our search strategy of electronic databases was comprehensive and developed with the help of the director of health sciences library of our institution. We combined this database search with a secondary hand-search of references lists of the included studies. Moreover, we conducted a fully transparent and reproducible review. Other researchers may freely reuse our data and scripts to conduct their own work or use our database to identify papers pertinent for their research projects.
